Reduced plasticity and variance in physiological rates for terrestrial ectotherm populations under climate change

### 2024-02-03 ms.qmd
First paragraph of discussion

Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011]. Here, we show that the relative variance $lnCVR_{Q_{10}}$ in physiological rates is expected to decrease for ectotherms as temperatures increase, but particularly so for terrestrial ectotherms (~28%). Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation (i.e., $lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs. 15% reduction in relative variance; *terrestrial*: no acclimation vs 28% reduction in relative variance; @fig-1). Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections. Our results provide a more complete picture of the impacts that climate warming will have on ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention. We discuss our findings in the context of the current literature and highlight key areas for future research.

>>>>

Understanding acclimation capacity and how variation in physiological rates change across populations and species is important for predicting the ecological and evolutionary consequences of climate change [@Chevin2017; @Chevin2010; @Bolnick2011]. Here, we show that the relative variance ($lnCVR_{Q_{10}}$) in physiological rates of ectotherms is expected to decrease for ectotherms as temperatures increase, and this decrease is particularly pronouced in terrestrial ectotherms (~28%). Decreases in the relative variance of physiological rates are equal to or larger than the expected benefits from acclimation ($lnRR_{Q_{10_{acclimation}}}$) in marine and terrestrial ectotherms (*marine*: 16% acclimation vs. 15% reduction in relative variance; *terrestrial*: no acclimation vs 28% reduction in relative variance; @fig-1). Such effects are expected to result in a decrease in the variability in physiological rates for marine and terrestrial ectotherms between ~4-13% under future climate change projections. Our results provide insight into the multifaceted ways in which climate warming will impact ectotherm populations, with important ecological and evolutionary implications that require further empirical and theoretical attention. We discuss our findings in the context of the current literature and highlight key areas for future research.
